---
title: "R Notebook"
output: html_notebook
---

### install tidyverse package
```{r}
install.packages("tidyverse")

```



### load all the necessary libraries
```{r}
library(tidyverse)
library(ggplot2)
```

### importing the data as a csv
```{r}
SB_History <- read.csv("Super_Bowl_History.csv")
SB_History
```


### subseting to get all the appearances for both teams in any superbowl
### whether they won or lost
```{r}
df1 <- subset(SB_History, AFC == "Kansas City Chiefs")
df2 <- subset(SB_History, NFC == "Kansas City Chiefs")
df3 <- subset(SB_History, AFC == "Tampa Bay Buccaneers")
df4 <- subset(SB_History, NFC == "Tampa Bay Buccaneers")

new_data <- filter(SB_History, AFC %in% c("Kansas City Chiefs", "Tampa Bay Buccaneers") , AFC %in% c("Kansas City Chiefs"  , "Tampa Bay Buccaneers"))  

ggplot(new_data, aes(x=AFC, y=winer.points,  fill=Date)) + 
  geom_bar(stat = "identity") +
labs(title = "Team Appearance and outcome throughout super bowl history" ,
subtitle = "Source: Super Bowl History Data" ,
x = "Team" ,
y = "Winning Points")


```


### importing the data as a csv
```{r}
Kansas_vs_Tampa_History <- read.csv("Tampa_vs_Kansas.csv")
Kansas_vs_Tampa_History
```

### subseting the data for more precision and accuracy
```{r}
df <- subset(Kansas_vs_Tampa_History, Home == "Tampa Bay Buccaneers")
ggplot(df, aes(x=Tampa.Bay.Points, y=Date,  fill = Winer)) + 
  geom_bar(stat = "identity") +
labs(title = "Tampa Bay Buccanners home game scores and outcome" ,
subtitle = "Source: Tampa Bay Buccanners Vs. Kansas City Chiefs " ,
x = "Score" ,
y = "Date")
```



### Violin Plots of the the score difference for each game
```{r}
ggplot(Kansas_vs_Tampa_History, aes(x = Winer, y = Difference, color = Winer)) + 
  geom_violin(show.legend = FALSE) +
   labs(title = "Point Difference between each match of Chiefs Vs. Buccanners ",
             subtitle = "Source: Tampa Bay Buccanners Vs. Kansas City Chiefs" ,
             x = "Team",
             y = "Point Difference") 
```



### importing the data as a csv
```{r}
S_History <- read.csv("spreadspoke_scores.csv")
S_History
```

### subseting to get all the appearances for both teams in any superbowl
### whether they won or lost
```{r}
df <- subset(S_History, team_home == "Kansas City Chiefs")
ggplot(S_History, aes(x=score_away, y= schedule_season,  fill=team_home)) + 
  geom_bar(stat = "identity", show.legend = FALSE) +
labs(title = "Kansas points for away games" ,
subtitle = "Source: Super Bowl Data" ,
x = "Winner points" ,
y = "Season")


```